### 2020-09-11 manuscript/manuscript.rmd
minor tweeks

Yuanning Li^1,3^, Xing-xing Shen^2,3^, Benjamin Evans^4^, Steven H.D. Haddock^5^, Antonis Rokas^3^ and Casey W. Dunn^1^*

@@

^5^Monterey Bay Aquarium Research Institute, Moss Landing, CA 95039, USA

\* Corresponding author, casey.dunn@yale.edu

@@

Benjamin Evans:
Steven H.D. Haddock: 0000-0001-9420-4482

>>>>

Yuanning Li^1,3^, Xing-xing Shen^2,3^, Benjamin Evans^4^, Antonis Rokas^3^ * and Casey W. Dunn^1^*

@@

\* Corresponding authors, antonis.rokas@vanderbilt.edu, casey.dunn@yale.edu

@@

Benjamin Evans: 0000-0003-2069-4938
